---
title: "Reproducing MHE"
author: "Fernando Hoces de la Guardia"
date: "4/5/2018"
output: html_document
---

```{r load packages, echo=FALSE, warning=FALSE, results='hide', message=FALSE}
# I recomend copying and pasting this chunk to every DD you build, just change the list of packages you need for your code to run.
# Loading required libraries
list.of.packages <- c("foreign", "stargazer", "sandwich", "haven", "ggplot2", "lfe")

# Chicking if library installed, installed if not. 
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos= "http://cran.cnr.berkeley.edu/") 

# Calling libraries 
lapply(list.of.packages, require, character.only = TRUE)
```

## Introduction  
I have no idea what Fernando is talking about. Will focus on the structure of the argument.   

We want to reproduce figure 524 (originally fig 3 in the paper) from [this paper](http://economics.mit.edu/files/589). Where we look at the effects of a treatment over a outcome. 


## Raw data: download and load  
We obtain the data from the author's website. 


```{r download data, eval=FALSE, echo=TRUE, warning=FALSE, results='hide', message=FALSE}
# Download the data and unzip it
download.file('http://economics.mit.edu/~dautor/outsourcingatwill_table7.zip', 
              'outsourcingatwill_table7.zip')
unzip('outsourcingatwill_table7.zip')
```   


```{r load data, echo=TRUE, warning=FALSE, results='hide', message=FALSE}
# Load the data
autor <- read.dta('table7/autor-jole-2003.dta')
```


The data downloaded data set contains `r length(unique(autor$year))` years (from `r min(autor$year)` to `r max(autor$year)`) and `r length(unique(autor$state))` states, for a total of `r dim(autor)[1]` observations.
